DATA 605 Week 9 Assignment

### 2019-03-30 DATA605/MSilva_Assign9.Rmd
Work on Assignment 9
More work on Assignment 9

@@

@@

@@

@@

>>>>

Since we are starting at 100 after day 1 the problem can be restated

$$P(X_1 + ... + X_{364} \geq 0)$$

$$X_1 + ... + X_{364} = N(364 \times 0, \sqrt{364} * \sqrt{\frac{1}{4}}) = N(0, 9.539392)$$

$$P(X_1 + X_2 + ... + X_{364} \geq 0) = Z_0 = \frac{0 - 0}{9.539392} = 0$$

Looking up a Z-Score of 0 gives a *probability of 0.5*

```{r}
pnorm(0/(sqrt(364)*.5), lower.tail = FALSE)
```

@@

$$P(X_1 + X_2 + ... + X_{364} \geq 10) = Z_{10} = \frac{10 - 0}{9.539392} = 1.048285$$

*The probability is 0.8527463*

```{r}
pnorm(10/(sqrt(364)*.5), lower.tail = FALSE)
```

@@

$$P(X_1 + X_2 + ... + X_{364} \geq 20) = Z_{20} = \frac{20 - 0}{9.539392} = 2.09657$$

*The probability is 0.9819842*

```{r}
pnorm(20/(sqrt(364)*.5), lower.tail = FALSE)
```

@@

The binomial function is $b(x, n, p) = \frac{n!}{x!(n-x)!}p^xq^{n-x}$ with $q=1-p$.

The moment generating function is:

$$Mx(t)=\sum_{x=0}^{n} e^{xt} \frac{n!}{x!(n-x)!}p^xq^{n-x} = \sum_{x=0}^{n} (pe^t)^x \frac{n!}{x!(n-x)!}q^{n-x} = (q+pe^t)^n$$

Taking the derivative of the function with respect to t

$$\frac{dM(t)}{dt} = pe^t n(q+pe^t)^{n-1}$$

Evaluating at t=0

$$E(x) = np(q+p)^{n-1} = np$$

To find the variance we need to find E(x2)

$$E(x^2) = np(q + p)^{n−2}(q + np) = np(q + np)$$

We can now find the variance

$$V = E(x^2) - (E(x))^2 = np(q + np) - (np)^2 = np(q+np) - n^2p^2 = npq$$

@@

First we need to get the moment generating function:

$$Mx(t) = \int_{-\infty}^\infty e^{tx}fx(x)dx = \int_0^\infty e^{tx}\lambda e^{-\lambda x}dx = \lambda \int_0^\infty e^{(t - \lambda)x}dx = \frac{\lambda}{t- \lambda}$$

Now that the moment function is found we can find the first and second moments

$$E(x) = \frac{\lambda}{(t- \lambda)^2}|_{t=0} = \frac{1}{\lambda}$$

Here's the variance:

$$V = E(x^2) = \frac{2\lambda}{(t- \lambda)^3}|_{t=0} = \frac{2}{\lambda^2}$$
